Algebraic File Synchronization: Adequacy and Completeness

### 2017-09-30 p2/axioms.tex
Stronger lemma about distant pairs
Improved text. Added definitions of construction/destruction commands.

So that we can describe the effects of commands in general,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we will investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
% For example, we will write
% $S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
%% monoid, but not free monoid
%% monoid: semigroup with identity element
%% Sequences of commands form a free semigroup
We write $\sets$ for the set of sequences of commands.
They form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which is defined on all filesystems and by definition leaves all filesystems unchanged.
\end{mydef}

\begin{mydef}[$\Dom{S}$ and $\Img{S}$]
For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$,
which is the set of filesystems $S$
(that is, the commands it contains in the given order)
does not break.

We write $\Img{S}$ to denote the image of the domain of the sequence $X$.
\end{mydef}

The following two relations 
(which echo the ones defined in \cite{NREC})
allow us to investigate sequences of commands independently of filesystems.
In the definitions, $A,B,S,T$ stand for arbitrary sequences.

\begin{mydef}[$\eqext$]
% Relation in the algebra
$A\eqext B$ means that $B$ \emph{extends} $A$,
% intended interpretation:
that is, they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS\in\Dom{A}: A\aFS=B\aFS$.
% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\cc T$.
% preorder: reflexive and transitive
% patial order: reflexive, transitive and antisymmetric (aRb & bRa => a=b) TODO
In other words, $\eqext$ is a preorder, and also a precongruence.
\end{mydef}

@@

\begin{mylem}
$A\equiv B$
iff $A$ and $B$ behave in the same way on
all filesystems, that is, $\forall \FS: A\aFS=B\aFS$.
\end{mylem}
\begin{proof}
If $\forall \FS: A\aFS=B\aFS$ then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
For the reverse statement we know $A\eqext B$ and $B\eqext A$.
$B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
Therefore, for every filesystem $\FS$ either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$ still holds.
\end{proof}

@@

\begin{mydef}[Construction pair]
A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
and the commands are one
of the following:
   \begin{gather*}
            \cbdaa{\nn}\cc  \cbfaa{n} \\
            \cbdaa{\nn}\cc  \cbdaa{n} \\
            \cfdaa{\nn}\cc  \cbfaa{n} \\
            \cfdaa{\nn}\cc  \cbdaa{n}
   \end{gather*}
\end{mydef}

\begin{myax}\label{ax_directchild_breaks}
All other commands on a child break every filesystem:
$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
and the pair is not a construction pair.
\end{myax}

\begin{mydef}[Destruction pair]
A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
of the following:
   \begin{gather*}
            \cfba{n}\cc  \cdba{\nn} \\
            \cfba{n}\cc  \cdfaa{\nn} \\
            \cdba{n}\cc  \cdba{\nn} \\
            \cdba{n}\cc  \cdfaa{\nn}
   \end{gather*}
\end{mydef}

\begin{myax}\label{ax_directparent_breaks}
All other commands on a parent break every filesystem:
$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
and the pair is not a destruction pair.
\end{myax}

@@

\begin{mydef}[$A\indep B$: Independent commands, sequences and sets]\label{def_indep}
Two commands $\cxynv$ and $\czwmv$ 
are independent, and we write $\cxynv\indep\czwmv$ if 
they commute and do not break all filesystems:
\[ \cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk. \]
For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
We also write $\alpha\indep B$ iff $\forall \beta\in B:\alpha\indep\beta$.
\end{mydef}

@@

\begin{mylem}\label{incomparable_is_independent}
Two different commands that are not assertion commands are independent iff the nodes they change are incomparable:
\[ \cxynv\indep\czwmv \Longleftrightarrow n\unrel m \]
if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
\end{mylem}
\begin{proof}
This is easy to show based on the output of the program that investigates the behavior of command pairs.
However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
in the following way.

>>>>

So that we can describe the effects of commands independently of filesystems,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
% For example, we will write
% $S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
%% monoid, but not free monoid
%% monoid: semigroup with identity element
%% Sequences of commands form a free semigroup
We write $\sets$ for the set of sequences of commands.
They form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which is defined on all filesystems and by definition leaves all filesystems unchanged.
\end{mydef}

\begin{mydef}[$\Dom{S}$ and $\Img{S}$]
For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$,
which is the set of filesystems $S$
(that is, the commands it contains in the given order)
is defined on, that is, it does not break.

We write $\Img{S}$ to denote the image of the domain of the sequence $S$.
\end{mydef}

The following two relations 
echo the ones defined in \cite{NREC}.
In the definitions, $A,B,S,T$ stand for arbitrary sequences.

\begin{mydef}[$\eqext$]
% Relation in the algebra
We write $A\eqext B$, or $B$ \emph{extends} $A$,
% intended interpretation:
to mean that they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS\in\Dom{A}: A\aFS=B\aFS$.
% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\cc T$.
% preorder: reflexive and transitive
% patial order: reflexive, transitive and antisymmetric (aRb & bRa => a=b) TODO
In other words, $\eqext$ is a preorder, and also a precongruence.
\end{mydef}

@@

\begin{mylem}
$A\equiv B$
iff $A$ and $B$ behave in the same way on
all filesystems, that is, $\forall \FS: A\aFS=B\aFS$.
\end{mylem}
\begin{proof}
% TODO APPENDIX
If $\forall \FS: A\aFS=B\aFS$, then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
For the reverse statement we know $A\eqext B$ and $B\eqext A$.
$B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
Therefore, for every filesystem $\FS$, either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$.
\end{proof}

% Rules
% -----

@@

\begin{mydef}[Construction pair]
A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
and the commands are one
of the following:
   \begin{gather*}
            \cbdaa{\nn}\cc  \cbfaa{n} \\
            \cbdaa{\nn}\cc  \cbdaa{n} \\
            \cfdaa{\nn}\cc  \caaa{\empt}{\valff}{n} \\
            \cfdaa{\nn}\cc  \cbdaa{n}
   \end{gather*}
\end{mydef}

\begin{mydef}[Construction command]
A command $\cxynv$ is a construction command if it can appear in a construction pair,
that is, if $[x]=[\empt]$ and $[y]=[\valf]$ or $[y]=[\vald]$,
or if $[x]=[\valf]$ and $[y]=[\vald]$.
\end{mydef}

\begin{myax}\label{ax_directchild_breaks}
All other commands on a child break every filesystem:
$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
and the pair is not a construction pair.
As we shall see, this can be extended to \cref{simple_distant_pairs}.
% TODO
\end{myax}

\begin{mydef}[Destruction pair]
A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
of the following:
   \begin{gather*}
            \cfba{n}\cc  \cdba{\nn} \\
            \cfba{n}\cc  \caaa{\vald}{\valff}{\nn} \\
            \cdba{n}\cc  \cdba{\nn} \\
            \cdba{n}\cc  \cdfaa{\nn}
   \end{gather*}
\end{mydef}

\begin{mydef}[Destruction command]
A command $\cxynv$ is a destruction command if it can appear in a destruction pair,
that is, 
if $[x]=[\valf]$ and $[y]=[\empt]$,
or if $[x]=[\vald]$ and $[y]=[\empt]$ or $[y]=[\valf]$.
Note that a command cannot be both a construction and a destruction command.
\end{mydef}

\begin{myax}\label{ax_directparent_breaks}
All other commands on a parent break every filesystem:
$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
and the pair is not a destruction pair.
This can also be extended to \cref{simple_distant_pairs}.
% TODO
\end{myax}

@@

\begin{mydef}[$A\indep B$: Independent commands, sequences and sets of commands]\label{def_indep}
Two commands $\cxynv$ and $\czwmv$ 
are independent, and we write $\cxynv\indep\czwmv$ if 
they commute and do not break all filesystems:
\[ \cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk. \]
For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
We also write $\alpha\indep B$ iff $\{\alpha\}\indep B$.
\end{mydef}

@@

\begin{mylem}\label{incomparable_is_independent}
Two different commands that are not assertion commands are independent iff the nodes they change are incomparable. In other words,
\[ \cxynv\indep\czwmv \Longleftrightarrow n\unrel m \]
if $\cxy\neq\czw$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
\end{mylem}
\begin{proof}
This is easy to show based on the output of the program that investigates the behavior of command pairs.
However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
in the following way.

### 2017-09-30 p2/def-commands.tex
Improved text. Added definitions of construction/destruction commands.

Let us consider what kind of information is usually encoded in filesystem operations.
A minimal set of commands, based on the most frequent tools implemented by filesystems,
may be the following, where 
$n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$):
\begin{itemize}
\item $create(n,\valv)$, which creates a file or directory ($\valv$) at $n$
where the file system contains no file or directory ($\empt$);
\item $edit(n,\valv)$, which replaces the earlier file or directory at $n$ with $\valv$;
\item $remove(n)$, which removes the file or directory at $n$, and replaces it with $\empt$.
\end{itemize}
Regarding their output, that is, the state of the filesystem at $n$
after applying the command,
we know that after $create$ or $edit$, $\FS(n)\neq\empt$, whereas after $remove$,
$\FS(n)$ will be $\empt$. 
However, from \cite{NREC} and \cite{CBNR} we know that a useful set of axioms
will in some cases need to distinguish between, for example,
$edit$s that result in directories ($edit(n,\vald)$) and
ones that result in files ($edit(n,\valf)$), and treat them as separate commands,
as their behaviors are quite different when combined with other commands.
Indeed, Bill Zissimopoulos' work
demonstrated \cite{BZ}
that extending this distinction to more commands ultimately simplifies
the definition of conflicting commands, as our model will then able to predict the behavior of commands
more precisely.
In other words, encoding the outputvalue in the commands is definitely useful.
As the success or failure of filesystem commands only depends on the types of values in the filesystem,
we expect to use the type of their output when modelling their behavior.

Notice, however, that the commands listed above also encode some information about 
their input, the state of the filesystem
before the command is applied. In particular, $create(n,\valv)$ requires that there are no files
or directories at $n$, while $edit(n,\valv)$ and $remove(n)$ require the opposite.
This creates an arbitrary asymmetry where
there is now more information available about their output than about their input.
As, based on the above, we expect that encoding more information in the commands
results in a model with greater predictive powers,
and in order to resolve this asymmetry, 
we propose a set of commands that encode
the type of the original value $\FS(n)$ as well.
(Some real-life filesystem commands like $rmdir$ do this already.)
Again, as the success of failure of commands depends on types of values,
it is not necessary to encode the actual input value.

% Break / empty command

\noindent
A command at times will return an error.
This happens if the encoded type of the original filesystem value does not match
what is actually in the filesystem, or if the modified filesystem no
longer has the tree property.
In these cases we say that the command {\em breaks} the filesystem,
and the function we use to model the command will be undefined on the filesystem.

So that we could reason about sequences of commands that break every filesystem, 
we also introduce the command $\cbrk$ which is not defined anywhere,
that is, which breaks every filesystem.

% Definition

\begin{mydef}[Filesystem commands]
In other words, we model filesystem commands as partial endofunctions on filesystems,
that is, functions that map filesystems to filesystems, but which
are not defined everywhere:
\[ \alpha: \setfs \nrightarrow \setfs \]
A command $\alpha$ is not defined on filesystems that it would break.
At times in these cases we write that the command returns the bottom element, $\fsbroken$.
We write $\cbrk$ for the empty partial function which is not defined anywhere.

@@

For example, $\cbfaa{n}$ will represent $create(n,\valf)$,
and $\cdba{n}$ will represent $rmdir(n)$.
When describing unknown commands, we substitute one or both
of their values with variables, and write e.g. $\cxynv$.
By $\cxynv=\czwmv$ we mean that the commands are identical
($[x]=[z]$ and $y=z$ and $n=m$).
As suggested above, we will frequently only investigate
the types of the input and output values of a command
(its input and output types), and write
$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$
(or equivalently $x\typeeq z$ and $y\typeeq w$).

>>>>

Let us consider what kind of information is usually encoded in filesystem operations.
A minimal set of commands, based on the most frequent tools implemented by filesystems,
may be the following, where 
$n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$):
\begin{itemize}
\item $create(n,\valv)$, which creates a file or directory ($\valv$) at $n$
where the file system contains no file or directory ($\empt$);
\item $edit(n,\valv)$, which replaces the earlier file or directory at $n$ with $\valv$;
\item $remove(n)$, which removes the file or directory at $n$, and replaces it with $\empt$.
\end{itemize}
Regarding their output, that is, the state of the filesystem at $n$
after applying the command,
we know that after $create$ or $edit$, $\FS(n)\neq\empt$, whereas after $remove$,
$\FS(n)$ will be $\empt$. 
However, from \cite{NREC} and \cite{CBNR} we know that a useful set of axioms
will in some cases need to distinguish between, for example,
$edit$s that result in directories ($edit(n,\vald)$) and
ones that result in files ($edit(n,\valf)$), and treat them as separate commands,
as their behaviors are quite different when combined with other commands.
Indeed, Bill Zissimopoulos' work
demonstrated \cite{BZ}
that extending this distinction to more commands ultimately simplifies
the definition of conflicting commands, as our model will then able to predict the behavior of commands
more precisely.
In other words, encoding the output value in the commands is definitely useful.
As the success or failure of filesystem commands only depends on the types of values in the filesystem,
we expect to use the type of their output when modelling their behavior.

Notice, however, that the commands listed above also encode some information about 
their input, the state of the filesystem
before the command is applied. In particular, $create(n,\valv)$ requires that there are no files
or directories at $n$, while $edit(n,\valv)$ and $remove(n)$ require the opposite.
This creates an arbitrary asymmetry where
there is now more information available about their output than about their input.
As, based on the above, we expect that encoding more information in the commands
results in a model with greater predictive powers,
and in order to resolve this asymmetry, 
we propose a set of commands that encode
the type of the input value $\FS(n)$ as well.
(Some real-life filesystem commands like $rmdir$ do this already.)
Again, as the success of failure of commands depends on types of values,
it is not necessary to encode the actual input value.

% Definition
% Break / empty command

\begin{mydef}[Filesystem commands, $\cbrk$]
We model filesystem commands as partial endofunctions on filesystems,
that is, functions that map filesystems to filesystems, but which
are not defined everywhere:
\[ \alpha: \setfs \nrightarrow \setfs \]
A command $\alpha$ is not defined on filesystems where it returns an error.
This happens if the input type of the command does not match
what is actually in the filesystem, or if the modified filesystem no
longer has the tree property.
At times in these cases we write that the command {\em breaks} the filesystem,
or that it returns the bottom element, $\fsbroken$.

We write $\cbrk$ for the empty partial function which is not defined anywhere.

@@

For example, $\cbfaa{n}$ represents $create(n,\valf)$,
and $\cdba{n}$ represents $rmdir(n)$.
When describing unknown commands, we substitute one or both
of their values with variables, and write e.g. $\cxynv$.
By $\cxynv=\czwmv$ we mean that the commands are identical
($[x]=[z]$ and $y=z$ and $n=m$).
As suggested above, we will frequently only investigate
the types of the input and output values of a command
(its input and output types), and write
$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$.

### 2017-09-30 p2/ordering.tex
Improved text. Added definitions of construction/destruction commands.

Let us therefore define $\ordersetsign$ which gives us all
possible orders in which a set of commands can be applied
to filesystems without breaking it
provided that the commands can be applied to a fileystem in some order.

\begin{mydef}[$\ordersetsign$]\label{def_orderset}
For a simple set or sequence $U$,
we use $\orderset{U}$ to denote the set of sequences
that are all permutations of the commands in $U$
for which the following holds:
for any two commands $\cxynv$ and $\czwmv$ in a permutation
where $\cxynv$ comes earlier,
\begin{itemize}
\item if $n=\parent(m)$, then $y=\vald$
\item if $\parent(n)=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

The principal ideas behind this algorithm are 
\cref{ax_separate_commute}, from which we know that commands on incomparable
nodes can be applied in any order, so we only need to focus on the order of commands
with comparable nodes;
\cref{connected_changes}, from which we know that if $U$ contains commands on two comparable
nodes, then it contains commands on all nodes in between, so it is enough to specify
the order of commands on directly related nodes;
and finally, \cref{ax_directchild_breaks,ax_directparent_breaks}, from which we know
that commands on parent--child pairs must be construction or destruction pairs.
Investigating these pairs we see that they are identified by the output value of the first command ($y$),
which in turn determines whether the command on the parent or the child must precede the other.

@@

\begin{mylem}\label{simple_distant_pairs}
For any simple sequence $S\nequiv\cbrk$
if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
then $\cxynv\cc\czwmv\nequiv\cbrk$.
\end{mylem}
\begin{proof}
As usual, by subsequence we mean a subset of the commands in $S$ in the same order as they are found in $S$.

Informally speaking, the proposition means that
the two commands must form a construction or destruction pair even
if they are not next to each other.
This is true because in simple sequences
there cannot be another command on $n$ or $m$,
so if the commands are incompatible, no command between them can change that.
In fact, this \namecref{simple_distant_pairs} is the general case
of \cref{ax_directchild_breaks,ax_directparent_breaks}.

% BACK_TO_THE_FS TODO
% TODO Review any proof depending on "nothing changes FS at n until...".
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
We assume $S\nequiv\cbrk$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
but it contains commands on a node and its parent that do not form a construction or destruction pair.
Select two such commands, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2 \]
As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.

@@

\begin{mycor}\label{order_is_only_possible}
For any simple sequence $S$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
it contains two commands on a node $n$ and its parent
that placed next to each other do not form
a construction or destruction pair.
Let them be $\cxynv$ and $\czwmv$.
By \cref{ax_directchild_breaks,ax_directparent_breaks}
we know the subsequence of $S'$,
$\cxynv\cc\czwmv\equiv\cbrk$ and therefore by \cref{simple_distant_pairs}
$S'\equiv\cbrk$.
\end{proof}

@@

Furthermore,
we prove this proposition for sequences, not sets, as if all sequences must contain a command on $\parent(n)$,
then so must all sets because otherwise there would be no order in which the commands they contain could be
applied to any filesystem.

@@

\begin{mylem}\label{simple_reorder_equiv}
For a simple sequence $S\nequiv\cbrk$,
\[ \orderset{S} = [S]_\equiv \cap \setssmp, \]
where $[S]_\equiv \cap \setssmp$ is the set of simple sequences equivalent to $S$.
\end{mylem}
\begin{proof}
First, we prove, by contradiction, that if a simple sequence $T\equiv S$, then $T\in\orderset{S}$.
We assume $T\equiv S$ and $T\not\in\orderset{S}$.
Then, from \cref{equiv_simple_same_commands} we know $T$ is a permutation of $S$,
and from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
is a contradiction as $T\equiv S\nequiv\cbrk$.

>>>>

Let us therefore define $\ordersetsign$ which gives all
permutations of a set of commands that do not break all filesystems.

\begin{mydef}[$\ordersetsign$]\label{def_orderset}
For a simple set or sequence of commands $U$,
we use $\orderset{U}$ to denote the set of sequences
that are all permutations of the commands in $U$
for which the following holds:
for all subsequences $\cxynv\cc\czwmv$,
\begin{itemize}
\item if $n=\parent(m)$, then $y=\vald$
\item if $\parent(n)=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

As usual, by subsequence we mean a subset of the commands in $S$ in the same order as they are found in $S$.

The principal ideas behind these conditions are 
\cref{ax_separate_commute}, from which we know that commands on incomparable
nodes can be applied in any order, so we only need to focus on the order of commands
with comparable nodes;
\cref{connected_changes}, from which we know that if $U$ contains commands on two comparable
nodes, then it contains commands on all nodes in between, so it is enough to specify
the order of commands on directly related nodes;
and finally, \cref{ax_directchild_breaks,ax_directparent_breaks}, from which we know
that commands on parent--child pairs must be construction or destruction pairs.
Investigating these pairs we see that they are identified by the output value of the first command ($y$),
which in turn determines whether the command on the parent or the child must precede the other.

@@

\begin{mylem}\label{simple_distant_pairs}
For any simple sequence $S\nequiv\cbrk$
if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
then $\cxynv\cc\czwmv\nequiv\cbrk$.
\end{mylem}
\begin{proof}
Informally speaking, the proposition means that
the two commands must form a construction or destruction pair even
if they are not next to each other.
This is true because in simple sequences
there cannot be another command on $n$ or $m$,
so if the commands are incompatible, no command between them can change that.
In fact, this \namecref{simple_distant_pairs} is the general case
of \cref{ax_directchild_breaks,ax_directparent_breaks}.

% BACK_TO_THE_FS TODO
% TODO Review any proof depending on "nothing changes FS at n until...".
% TODO Move to rules
% TODO APPENDIX
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
We assume $S\nequiv\cbrk$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
but $S$ contains commands on a node and its parent that do not form a construction or destruction pair.
Select two such commands, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2. \]
As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.

@@

\begin{mycor}\label{order_is_only_possible}
For any simple sequence $S$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
it contains two commands on a node $n$ and its parent
that placed next to each other do not form
a construction or destruction pair.
Let them be $\cxynv$ and $\czwmv$.
By \cref{ax_directchild_breaks,ax_directparent_breaks}
we know
$\cxynv\cc\czwmv\equiv\cbrk$, which is a subsequence of $S'$,
and therefore by \cref{simple_distant_pairs} $S'\equiv\cbrk$.
\end{proof}

@@

Furthermore,
we prove this proposition for sequences, not sets, as if all sequences must contain a command on $\parent(n)$,
then so must all sets because otherwise there would be no order in which the commands they contain could be
applied to a filesystem.

@@

\begin{mylem}\label{simple_reorder_equiv}
For a simple sequence $S\nequiv\cbrk$,
$\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
\[ \orderset{S} = [S]_\equiv \cap \setssmp. \]
\end{mylem}
\begin{proof}
First, we prove, by contradiction, that if a simple sequence $T\equiv S$, then $T\in\orderset{S}$.
We assume $T\equiv S$ and $T\not\in\orderset{S}$.
Then, from \cref{equiv_simple_same_commands} we know $T$ is a permutation of $S$,
and from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
is a contradiction as $T\equiv S\nequiv\cbrk$.
